---
title: "Day 1 - R Stan Workshop @ Calvin College"
author: "Seun Odeyemi"
date: "6/10/2019"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Libraries

```{r stan-libraries, message=TRUE, warning=TRUE}
library(rstan)
library(rstanarm)
library(bayesplot)
```


## Visualization in Bayesian Workflow

1. Exploratory data analysis: We look at the data thinking about the models we want to fit.
2. Prior predictive checking: This will help analyze assumptions you are making in the prior before fitting the model. 
3. Model fitting and algorithm diagnostics
4. Posterior predictive checking: Checking inferences 
5. Model comparison (e.g., via cross-validation)




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
